Automated topic naming to support analysis of software maintenance activities

### 2010-08-21 icse/icse2011.tex
threats to validity read and edit

\textbf{Do the different projects differ in their relative topic interest?} -- 
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} and \emph{portability} related topics.
 In both cases portability was a constant maintenance concern and was prevalent throughout the entire lifetime of the projects.
\todo[inline]{fix}

@@

If the techniques used in \textsf{exp2} and \textsf{exp3} were combined with the supervised techniques we could probably reduce the training effort by boosting training sets with topics classified with the unsupervised techniques.
Both Naive Bayesian learners and the word-list approaches were computationally efficient.  
%These results are promising, because the accuracy of the techniques is good enough to be useful, while the run-time performance is still cheap enough to execute to be feasible as an automated or semi-automated method of labelling topics by their software qualities.
These results are promising because they indicate that these techniques are accurate enough to be useful while still maintaining acceptable run-time performance.

@@

% can always be cut down

\emph{Construct validity} -- we used only commit messages rather than mail or bug tracker messages. 
Conversely, construct validity was addressed in our validation as we used the files, topics and revisions to annotate the commit messages.
We also chose our taxonomy and the data to study. We did not show these results to the stakeholders.

\emph{Internal validity} -- include inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model or theory.

@@

%\todo[inline]{update this with more detail}

@@

The idea of extracting higher-level `concerns', also known as `concepts', `aspects' or `requirements', has been approached from documentation-based and repositories-based perspectives.

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our worked differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison, which was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured that the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.

>>>>

\textbf{Do the different projects differ in their relative topic interest?} -- 
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} and \emph{portability} related topics.
 In both cases portability was a constant maintenance concern and was prevalent throughout the entire lifetime of the projects.
% XXX fix?
%\todo[inline]{fix}

@@

If the techniques used in \textsf{exp2} and \textsf{exp3} were combined with the supervised techniques we could reduce the training effort by boosting training sets with topics classified with the unsupervised techniques.
Both Naive Bayesian learners and the word-list approaches were computationally efficient.  
%These results are promising, because the accuracy of the techniques is good enough to be useful, while the run-time performance is still cheap enough to execute to be feasible as an automated or semi-automated method of labelling topics by their software qualities.
These results are promising because they indicate that these techniques are accurate enough to be useful while still maintaining acceptable run-time performance.

@@

% can always be cut down
Our work faced multiple threats to validity and we attempted to address many of them.

\emph{Construct validity} -- we used only commit messages rather than mail or bug tracker messages. 
Conversely, construct validity was addressed in our validation as we used the files, topics and revisions to annotate the commit messages. 
We used mailing-lists to verify the purpose behind some events.
We also chose our taxonomy and the data to study. We did not show these results to the stakeholders.

\emph{Internal validity} -- includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model or theory.

@@

@@

The idea of extracting higher-level `concerns', also known as `concepts', `aspects' or `requirements', has been approached from documentation-based and repository-based perspectives.

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed a recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our worked differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison, which was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured that the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.
